### 2018-04-26 1_intro.tex
Consider Prof. Heljanko's comments.

\begin{figure}
\small \ttfamily
\begin{tabular}{ |l|l| }
\hline
\multicolumn{2}{|l|}{ \{ x=0; y=0; \}} \tabularnewline \hline
P0 & P1 \\ \hline
MOV [x],1 & MOV [y],1 \\
MOV EAX,[y] & MOV EAX,[x] \\
\hline
%\multicolumn{2}{|l|}{locations [x;y;]} \tabularnewline
\multicolumn{2}{|l|}{exists (0:EAX=0~/\textbackslash~1:EAX=0)} \tabularnewline
\hline
\multicolumn{2}{|l|}{x86-TSO: allow} \tabularnewline
\hline

@@

Most modern high-level programming languages rely on relaxed memory model as well.
Thus, the memory model for Java that is based on the \textit{happens-before} principle~\cite{lamport1978time} was introduced in J2SE 5.0 in 2004~\cite{manson2005java}; the C++11 standard~\cite{?} has introduced the set of hardware-independent synchronisation fences and atomic operations, whenever the C++17 memory model~\cite{batty2011mathematizing} is based on the relation \textit{strongly happens-before}. Weak memory are being formalised for even more abstract software environments, the notable project in this area is the project on formalising the Linux kernel memory model, which is being actively developing these days~\cite{kernel1}.
Furthermore, there is a wide range of tools that perform program verification wrt memory models (see~\cite{alglave2013software}, \cite{Porthos17}).

>>>>

\begin{figure}
\centering
\ttfamily
\begin{tabular}{ |l|l| }
\hline
\multicolumn{2}{|l|}{ \{ x=0; y=0; \}} \tabularnewline \hline
P0 & P1 \\ \hline
MOV [x],1 & MOV [y],1 \\
MOV EAX,[y] & MOV EAX,[x] \\
\hline
%\multicolumn{2}{|l|}{locations [x;y;]} \tabularnewline
\multicolumn{2}{|l|}{exists (0:EAX=0~/\textbackslash~1:EAX=0)} \tabularnewline
\hline
\multicolumn{2}{|l|}{x86-TSO: allow} \tabularnewline
\hline

@@

Most modern high-level programming languages rely on relaxed memory model as well.
Thus, the memory model for Java is based on the \textit{happens-before} principle~\cite{lamport1978time}, it was introduced in J2SE 5.0 in 2004~\cite{manson2005java}; the C++11 standard~\cite{iso2012iec} has introduced the set of hardware-independent synchronisation fences and atomic operations, whenever the C++17 memory model~\cite{batty2011mathematizing} is based on the relation \textit{strongly happens-before}. Weak memory are being formalised for even more abstract software environments, the notable project in this area is the project on formalising the Linux kernel memory model, which is being actively developing these days~\cite{kernel1}.
Furthermore, there is a wide range of tools that perform program verification wrt memory models (see~\cite{alglave2013software}, \cite{Porthos17}).
